### 2025-04-24 latex/draft.tex
draft

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}

\title{Your Title Here}
\author{Your Name}
\date{\today}

\begin{document}

\maketitle

\section{Introduction}
This is the introduction section

\section{Methods}
This section describes the methods used

\section{Results}
This section presents the results

\section{Discussion}
This section discusses the results

\section{Conclusion}
This is the conclusion section

\bibliographystyle{plain}
\bibliography{references}

\end{document}

### 2025-05-07 latex/draft.tex
开始写论文

@@
 \usepackage{graphicx}
+\usepackage[style=authoryear, backend=biber]{biblatex} % 使用biblatex
+\addbibresource{references.bib} % 确保你的.bib文件名称正确
 
@@
 \section{Introduction}
-This is the introduction section
+
+  Modern logistics has evolved into a vital enabler of global economic integration, facilitating the seamless flow of goods across production, distribution, and consumption networks.
+Driven by technological innovation and sustainability imperatives, the industry is undergoing transformative shifts.
+Recent advancements emphasize the integration of automation and artificial intelligence, with smart warehouses and real-time tracking systems significantly enhancing operational efficiency (\cite{WOS001352081800001}).
+Concurrently, green logistics initiatives are reshaping traditional practices, prioritizing energy-efficient transportation and recyclable materials to align with global environmental goals (\cite{WOS:000693009900004}).
+
+Drone technology has achieved significant breakthroughs in autonomous navigation and operational capabilities through recent advancements.
+Modern systems employ multi-sensor fusion architectures combining LiDAR, visual SLAM, and millimeter-wave radar to achieve centimeter-level positioning accuracy in GNSS-denied environments  (\cite{WOS:001140699200001}).
+The introduction of hydrogen fuel cells have significantly extended operational endurance, overcoming traditional limitations while maintaining eco-friendly profiles  (\cite{WOS:001139514900001}).
+
+Artificial intelligence has revolutionized drone capabilities, empowering intelligent swarm coordination and real-time environmental adaptation.
+Vision-based navigation techniques enable dynamic route optimization and obstacle avoidance, particularly valuable for tasks like precision agriculture and infrastructure inspection  (\cite{WOS:000939165400001}).
+Communication breakthroughs, such as 5G-enabled edge computing, provide ultra-low latency control essential for beyond visual line of sight operations and urban air mobility networks  (\cite{WOS:001055864000001}).
+
+Drone technology is reshaping logistics paradigms by introducing aerial solutions to longstanding terrestrial constraints.
+Unlike conventional delivery methods constrained by road infrastructure, drones leverage low-altitude airspace to establish direct point-to-point connections.
+This capability proves transformative for last-mile delivery, particularly in geographically challenging regions where traditional transport faces inefficiencies (\cite{WOS:001404731600001}).
+By integrating multi-sensor navigation systems and hybrid propulsion technologies, drones enable time-sensitive pharmaceutical deliveries to remote clinics, emergency parts distribution for offshore wind farms, and precision inventory management in smart warehouses (\cite{WOS:001262605900001}).
+Their ability to bypass terrestrial bottlenecks complements existing logistics networks, creating layered delivery ecosystems where aerial routes dynamically adjust to real-time demand fluctuations.
+This shift not only addresses critical gaps in rural and urban last-mile logistics but also drives sustainable practices through energy-efficient operations, positioning drones as catalytic enablers for next-generation supply chain resilience.
+
+In the field of drone logistics, literature reviews also play a critical role in synthesizing interdisciplinary advancements, identifying operational gaps, and guiding future research.
+For instance, Kim et al.
+(\cite{WOS:001323645000001}) employs text-mining techniques to map two decades of research in drone-assisted multimodal logistics, revealing distinct emphases in drone-truck, drone-ship, and drone-robot systems while highlighting latent topics like energy efficiency and regulatory alignment.
+Moshref-Javadi and Winkenbach’s framework highlights systemic gaps in multi-drone coordination and resupply dynamics, revealing a disconnect between academic focus on single-drone systems and real-world requirements for complex fleet coordination  (\cite{WOS:000693999200007}).
+Jazairy et al.’s systematic review bridges logistics management and technical research by evaluating drone potentials across 12 last-mile criteria, such as payload adaptability and noise reduction, while proposing stakeholder-specific solutions like privacy-preserving geofencing for regulators (\cite{WOS:001160422800001}).Jahani et al.’s  review employs text-mining to map drone applications across supply chains, identifying critical gaps in holistic integration studies.
+Their analysis reveals emerging priorities like sustainable logistics networks and multimodal traffic coordination, while emphasizing the need for pandemic-responsive delivery frameworks (\cite{WOS:001262605900001}).
+Law et al.’s review evaluates drone applications in healthcare logistics, emphasizing their transformative potential in crisis response while identifying key barriers such as regulatory fragmentation and public trust  (\cite{WOS:000999662500001}).
+
+Bibliometrics, which employs quantitative methods to analyze research trends and knowledge structures across disciplines, has become pivotal in mapping technological innovations like drone applications.
+A seminal study by Fayyad et al.
+(2025) A Scientometric Analysis of Drone-Based Structural Health Monitoring and New Technologies identifies four research clusters in drone-enabled infrastructure monitoring, emphasizing AI integration and automation gaps while projecting breakthroughs in digital twins and robotics.
+Rejeb et al.
+(2022) in Drones in Agriculture: A Review and Bibliometric Analysis reveal dominant themes like precision farming and IoT integration, highlighting remote sensing and deep learning as key drivers reshaping agricultural efficiency.
+Similarly, Iqbal et al.
+(2023) in Drones for Flood Monitoring, Mapping and Detection map global research trajectories through bibliometric networks, stressing computer vision and real-time data fusion as critical for enhancing disaster response frameworks.
+For forestry applications, da Silva et al.
+(2024) in Using Drones for Dendrometric Estimations demonstrate UAVs' superiority over traditional methods in measuring tree height and biomass, with RGB sensors emerging as the primary tool for cost-effective forest management.
+These studies collectively underscore bibliometrics' role in crystallizing interdisciplinary advancements, identifying implementation barriers (e.g., regulatory fragmentation in healthcare logistics), and prioritizing future research directions like sustainable multimodal integration and AI-driven scalability.
 
@@
 
-\bibliographystyle{plain}
-\bibliography{references}
+\printbibliography
 

### 2025-05-08 latex/draft.tex
更新论文

@@
 
-Bibliometrics, which employs quantitative methods to analyze research trends and knowledge structures across disciplines, has become pivotal in mapping technological innovations like drone applications.
-A seminal study by Fayyad et al.
-(2025) A Scientometric Analysis of Drone-Based Structural Health Monitoring and New Technologies identifies four research clusters in drone-enabled infrastructure monitoring, emphasizing AI integration and automation gaps while projecting breakthroughs in digital twins and robotics.
+Bibliometrics, a quantitative research method that employs statistical and computational techniques to analyze publication patterns, citation networks, and knowledge evolution within academic domains, serves as a critical tool for mapping interdisciplinary advancements and identifying emerging trends.
+Its significance lies in synthesizing fragmented research landscapes, revealing collaborative networks, and prioritizing future directions through metrics such as co-citation analysis, keyword clustering, and temporal trend mapping (\cite{WOS:000958189000001}).
+Within drone technology research, several studies demonstrate the application of bibliometric approaches to map interdisciplinary knowledge domains.
+For instance, Fayyad et al.
+(\cite{WOS:001229751500001}) utilize scientometric analysis to categorize drone-based structural health monitoring (SHM) into four research clusters.
 Rejeb et al.
-(2022) in Drones in Agriculture: A Review and Bibliometric Analysis reveal dominant themes like precision farming and IoT integration, highlighting remote sensing and deep learning as key drivers reshaping agricultural efficiency.
-Similarly, Iqbal et al.
-(2023) in Drones for Flood Monitoring, Mapping and Detection map global research trajectories through bibliometric networks, stressing computer vision and real-time data fusion as critical for enhancing disaster response frameworks.
-For forestry applications, da Silva et al.
-(2024) in Using Drones for Dendrometric Estimations demonstrate UAVs' superiority over traditional methods in measuring tree height and biomass, with RGB sensors emerging as the primary tool for cost-effective forest management.
-These studies collectively underscore bibliometrics' role in crystallizing interdisciplinary advancements, identifying implementation barriers (e.g., regulatory fragmentation in healthcare logistics), and prioritizing future research directions like sustainable multimodal integration and AI-driven scalability.
+(\cite{WOS:000830895100002})) identify remote sensing, precision agriculture, and IoT as dominant themes in agricultural drone studies, while co-citation analysis reveals six research clusters.
+Iqbal et al.
+(\cite{WOS:000914960100001})) highlight evolving priorities in drones for flood management, emphasizing computer vision and real-time detection systems.
+Da Silva et al.
+(\cite{WOS:001366904300001})) employ bibliometrics to reveal that UAVs are increasingly used over traditional forest inventories to efficiently assess variables like tree height, DBH, biomass, and canopy area through high-resolution sensors.
+While prior bibliometric reviews like "Analyzing Forklift and Drone Applications in Sustainable Logistics" (\cite{WOS:001329532200078})) provide initial insights into drone logistics, their broad scope—spanning both forklifts and drones—and exclusive focus on sustainability limit granular analysis of drone-specific logistics.
+In addition, this study remains confined to quantitative metrics, without in-depth review of the literature.
+It also relies on keyword-based search on data collection, which can be improved by manual screening of the search results.
+Our study addresses these gaps through a dedicated drone logistics bibliometric analysis, combining quantitative bibliometrics with qualitative analysis of domain-specific innovations.
+
+The primary objective of this bibliometric study is to systematically map and evaluate the intellectual landscape of drone logistics research, focusing on its evolution, thematic priorities, and collaborative networks.
+To address this aim, the analysis integrates performance metrics (publication trends, citation impact, leading countries/institutions, prominent journals, and dominant Web of Science categories) with science mapping techniques (keyword co-occurrence, co-authorship networks, bibliographic coupling, and citation dynamics) using data extracted from Scopus and Web of Science.
+Central research questions include:
+
+(1) Identification of seminal publications and key contributors shaping the foundation of drone logistics research​.
+(2) Semantic clustering of research streams and thematic evolution in the field of drone logistics.
+(3) Temporal dynamics of collaboration networks and emerging frontiers​ in drone logistics research​.
+
+The paper is structured as follows: The methods section​​ details the data collection protocol, including database selection, search queries, inclusion/exclusion criteria, and analytical tools.
+The results section​​ presents bibliometric outputs: temporal publication trends, leading contributing countries, high-impact journals, and keyword co-occurrence clusters.
+​​The discussions​ section integrates these metrics with a qualitative synthesis of key literature, categorizing the field into subdomains and evaluating their interconnections, gaps, and evolution over time.
+The conclusions section​​ summarizes the findings of the study, acknowledges limitations and proposes future research directions.
 
 \section{Methods}
-This section describes the methods used
+\subsection{Data Collection} 
+这是数据收集部分的详细内容...
 

### 2025-05-08 latex/draft.tex
更新论文

@@
 
-(1) Identification of seminal publications and key contributors shaping the foundation of drone logistics research​.
+(1) Identification of seminal publications and key contributors shaping the foundation of drone logistics research.
 (2) Semantic clustering of research streams and thematic evolution in the field of drone logistics.
-(3) Temporal dynamics of collaboration networks and emerging frontiers​ in drone logistics research​.
+(3) Temporal dynamics of collaboration networks and emerging frontiers in drone logistics research.
 
-The paper is structured as follows: The methods section​​ details the data collection protocol, including database selection, search queries, inclusion/exclusion criteria, and analytical tools.
-The results section​​ presents bibliometric outputs: temporal publication trends, leading contributing countries, high-impact journals, and keyword co-occurrence clusters.
-​​The discussions​ section integrates these metrics with a qualitative synthesis of key literature, categorizing the field into subdomains and evaluating their interconnections, gaps, and evolution over time.
-The conclusions section​​ summarizes the findings of the study, acknowledges limitations and proposes future research directions.
+The paper is structured as follows: The methods section details the data collection protocol, including database selection, search queries, inclusion/exclusion criteria, and analytical tools.
+The results section presents bibliometric outputs: temporal publication trends, leading contributing countries, high-impact journals, and keyword co-occurrence clusters.
+The discussions section integrates these metrics with a qualitative synthesis of key literature, categorizing the field into subdomains and evaluating their interconnections, gaps, and evolution over time.
+The conclusions section summarizes the findings of the study, acknowledges limitations and proposes future research directions.
 
 \section{Methods}
-\subsection{Data Collection} 
-这是数据收集部分的详细内容...
+\subsection{Data Collection} % 二级标题
+Data extraction was conducted via the Web of Science (WOS) Core Collection.
+The search strategy combined drone-related terms (TS=("drone*" OR "Unmanned Aerial Vehicle" OR "UAV" OR "Unmanned Aerial System" OR "UAS")) with logistics-focused queries (TS=("logistic*" OR "transport*" OR "supply chain*" OR "delivery" OR "warehouse*")) using the Boolean operator AND, executed on April 1, 2025, yielding 5,649 initial records.
+Manual screening of titles and abstracts excluded 3,833 publications irrelevant to drone logistics applications (e.g., agricultural monitoring, cinematography).
+The final dataset comprised 1,816 papers, with metadata fields (authors, institutions, keywords, citations) exported for bibliometric processing.
 

### 2025-05-13 latex/draft.tex
更新论文

@@
 \section{Results}
-This section presents the results
+\subsection{Publication Volume}
+ The analysis of annual publication counts reveals distinct patterns in research activity within this field.
+From 1997 to 2017, annual outputs remained below 20 publications, with initial stagnation (1 publication in 1997, fluctuating between 2–18 until 2017).
+A marked acceleration began in 2018, as publications surged from 42 to 450 by 2024, corresponding to a compound annual growth rate (CAGR) of 48\% over this six-year period.
+Annual growth rates varied significantly, peaking at 114\% between 2019–2020 (71→152 publications), followed by gradual moderation in percentage terms.
+Absolute annual increments exceeded 30 publications after 2020, reaching a maximum increase of 104 publications from 2023 to 2024 (346→450).
+These quantitative metrics demonstrate a sustained expansion of research engagement post-2018, with publication volume increasing 10.7-fold between 2018 and 2024.
+
+\subsection{Keywords}
+"A systematic analysis of keyword frequencies in drone logistics literature identifies three principal categories: (1) Platform terminology with drone (347) and unmanned aerial vehicle (316) as dominant descriptors, accompanied by operational concerns like energy consumption (23) and urban air mobility (24); (2) Navigation methodologies where routing (90) and path planning (57) form the core, supported by established optimization frameworks including vehicle routing problem (27) and traveling salesman problem (24); (3) Application contexts led by logistics (80) and drone delivery (79), with last-mile delivery (50) and parcel delivery (23) as specialized sub-themes.
+This keyword distribution pattern shows delivery applications exhibit fewer distinct high-frequency descriptors compared to platform technologies and navigation algorithms, where drone (347), unmanned aerial vehicle (316), routing (90), and their derivative terms form a denser lexical network.
+
+\subsection{Authors}
+Our analysis of highly cited authors in the drone logistics domain reveals ​​Jinsoo Hwang​​ from Sejong University as the most highly-cited scholar, with a total citation count of ​​1,434​​.
+Hwang’s research focuses on consumer behavior and technology adoption in drone food delivery services, with his seminal works addressing critical dimensions of service innovation (\cite{WOS:000478712400012}), risk perception (\cite{WOS:000495004400013}), and behavioral adoption (\cite{WOS:000605628800016}).
+Our analysis further identifies ​​Chase C.
+Murray​​ from Auburn University as the second most influential scholar in drone logistics, with a total citation count of ​​1,209​​.
+Murray’s research pioneers operational optimization in drone-assisted delivery systems, particularly through algorithmic innovations for truck-drone coordination, epitomized by his ​​seminal work​​ "The flying sidekick traveling salesman problem: Optimization of drone-assisted parcel delivery" (\cite{WOS:000353871700006}).
+To our knowlege, it is ​​the first study to formalize the synchronized truck-drone routing problem as a novel variant of the vehicle routing problem (VRP).
+Stefan Poikonen from the University of Colorado Denver made contributions to drone logistics through his research on ​​vehicle routing problems with drones (VRPD)​​.
+His work set up theoretical frameworks for optimizing truck-drone coordination systems, introducing ​​worst-case analyses (\cite{WOS:000400384200003}) and ​​branch-and-bound algorithms (\cite{WOS:000468604000010}) to address operational challenges like synchronization and endurance constraints.
+​​Seokcheon Lee​​ from Purdue University has advanced drone logistics through innovative models for ​​truck-drone coordinated delivery systems​​, focusing on scalability and real-world constraints.
+His work "Multiple traveling salesman problem with drones: Mathematical model and heuristic approach" (\cite{WOS:000460496000002}) introduced a ​​multi-truck-drone routing framework​​ using mixed-integer programming and heuristics to minimize delivery times.
+He further addressed ​​payload-energy dependency​​ and ​​No-Fly Zones​​ (\cite{WOS:000474324300017}), integrating battery life constraints and regulatory airspace restrictions.
+Kevin ​​Dorling, Jordan Heinrichs, Jordan Messier, and Sebastian Magierowski​​ advanced drone routing by developing ​​multi-trip VRPs​​ that optimize energy consumption models (payload/battery weight) and enable ​​drone reuse​​.
+Their work introduced ​​mixed-integer programs​​ and ​​simulated annealing heuristics​​, revealing inverse exponential cost-time tradeoffs and offering tools to balance delivery efficiency and budget constraints (\cite{WOS:000623397300001}).
+While individual contributions remain pivotal, several highly cited scholars in drone logistics have achieved prominence through ​​collaborative partnerships​​.
+For example, ​​Amanda G.
+Chu's citation impact stems largely from co-authoring ​​Chase C.
+Murray's foundational work on truck-drone routing optimization  (\cite{WOS:000353871700006}).
+Similarly, ​​Jinkyung Jenny Kim​​’s influential studies on consumer behavior in drone food delivery emerged from collaborations with ​​Jinsoo Hwang (\cite{WOS:000514800800001, WOS:000605628800016, WOS:000623397300001})​​, while ​​Bruce Golden​​’s theoretical advances in vehicle routing problems with drones were co-developed with ​​Stefan Poikonen(\cite{WOS:000400384200003, WOS:000468604000010})​​.
 

### 2025-05-13 latex/draft.tex
更新论文

--- 2025-05-08 latex/draft.tex
@@
 \section{Results}
-This section presents the results
+\subsection{Publication Volume}
+ The analysis of annual publication counts reveals distinct patterns in research activity within this field.
+From 1997 to 2017, annual outputs remained below 20 publications, with initial stagnation (1 publication in 1997, fluctuating between 2–18 until 2017).
+A marked acceleration began in 2018, as publications surged from 42 to 450 by 2024, corresponding to a compound annual growth rate (CAGR) of 48\% over this six-year period.
+Annual growth rates varied significantly, peaking at 114\% between 2019–2020 (71→152 publications), followed by gradual moderation in percentage terms.
+Absolute annual increments exceeded 30 publications after 2020, reaching a maximum increase of 104 publications from 2023 to 2024 (346→450).
+These quantitative metrics demonstrate a sustained expansion of research engagement post-2018, with publication volume increasing 10.7-fold between 2018 and 2024.
+
+\subsection{Keywords}
+"A systematic analysis of keyword frequencies in drone logistics literature identifies three principal categories: (1) Platform terminology with drone (347) and unmanned aerial vehicle (316) as dominant descriptors, accompanied by operational concerns like energy consumption (23) and urban air mobility (24); (2) Navigation methodologies where routing (90) and path planning (57) form the core, supported by established optimization frameworks including vehicle routing problem (27) and traveling salesman problem (24); (3) Application contexts led by logistics (80) and drone delivery (79), with last-mile delivery (50) and parcel delivery (23) as specialized sub-themes.
+This keyword distribution pattern shows delivery applications exhibit fewer distinct high-frequency descriptors compared to platform technologies and navigation algorithms, where drone (347), unmanned aerial vehicle (316), routing (90), and their derivative terms form a denser lexical network.
+
+\subsection{Authors}
+Our analysis of highly cited authors in the drone logistics domain reveals Jinsoo Hwang from Sejong University as the most highly-cited scholar, with a total citation count of 1,434.
+Hwang’s research focuses on consumer behavior and technology adoption in drone food delivery services, with his seminal works addressing critical dimensions of service innovation (\cite{WOS:000478712400012}), risk perception (\cite{WOS:000495004400013}), and behavioral adoption (\cite{WOS:000605628800016}).
+Our analysis further identifies Chase C.
+Murray from Auburn University as the second most influential scholar in drone logistics, with a total citation count of 1,209.
+Murray’s research pioneers operational optimization in drone-assisted delivery systems, particularly through algorithmic innovations for truck-drone coordination, epitomized by his seminal work "The flying sidekick traveling salesman problem: Optimization of drone-assisted parcel delivery" (\cite{WOS:000353871700006}).
+To our knowlege, it is the first study to formalize the synchronized truck-drone routing problem as a novel variant of the vehicle routing problem (VRP).
+Stefan Poikonen from the University of Colorado Denver made contributions to drone logistics through his research on vehicle routing problems with drones (VRPD).
+His work set up theoretical frameworks for optimizing truck-drone coordination systems, introducing worst-case analyses (\cite{WOS:000400384200003}) and branch-and-bound algorithms (\cite{WOS:000468604000010}) to address operational challenges like synchronization and endurance constraints.
+Seokcheon Lee from Purdue University has advanced drone logistics through innovative models for truck-drone coordinated delivery systems, focusing on scalability and real-world constraints.
+His work "Multiple traveling salesman problem with drones: Mathematical model and heuristic approach" (\cite{WOS:000460496000002}) introduced a multi-truck-drone routing framework using mixed-integer programming and heuristics to minimize delivery times.
+He further addressed payload-energy dependency and No-Fly Zones (\cite{WOS:000474324300017}), integrating battery life constraints and regulatory airspace restrictions.
+Kevin Dorling, Jordan Heinrichs, Jordan Messier, and Sebastian Magierowski advanced drone routing by developing multi-trip VRPs that optimize energy consumption models (payload/battery weight) and enable drone reuse.
+Their work introduced mixed-integer programs and simulated annealing heuristics, revealing inverse exponential cost-time tradeoffs and offering tools to balance delivery efficiency and budget constraints (\cite{WOS:000623397300001}).
+While individual contributions remain pivotal, several highly cited scholars in drone logistics have achieved prominence through collaborative partnerships.
+For example, Amanda G.
+Chu's citation impact stems largely from co-authoring Chase C.
+Murray's foundational work on truck-drone routing optimization  (\cite{WOS:000353871700006}).
+Similarly, Jinkyung Jenny Kim’s influential studies on consumer behavior in drone food delivery emerged from collaborations with Jinsoo Hwang (\cite{WOS:000514800800001, WOS:000605628800016, WOS:000623397300001}), while Bruce Golden’s theoretical advances in vehicle routing problems with drones were co-developed with Stefan Poikonen(\cite{WOS:000400384200003, WOS:000468604000010}).
+
+\subsection{Citation analysis}
+Our analysis of the most highly cited drone logistics literature begins with the ​​top two papers​​—Murray et al.'s "The flying sidekick traveling salesman problem: Optimization of drone-assisted parcel delivery" (\cite{WOS:000353871700006}) and Dorling et al.'s "Vehicle Routing Problems for Drone Delivery" (\cite{WOS:000623397300001})—both previously detailed in discussions of their authors' contributions.
+Moving to next highly cited works: ​​Menouar et al.'s "UAV-Enabled Intelligent Transportation Systems for the Smart City: Applications and Challenges" (\cite{WOS:000398037700003}) maps UAV applications in urban mobility, identifying key challenges like airspace regulation and cybersecurity for smart-city integration.
+​​Büyüközkan & Gocer's "Digital Supply Chain: Literature review and a proposed framework for future research" (\cite{WOS:000432504700016}) frames drones as a pillar of digitized supply chains, emphasizing their role in agility and IoT-driven automation.
+Agatz et al.'s "Optimization Approaches for the Traveling Salesman Problem with Drone" (\cite{WOS:000442591800013})​​ formalizes the ​​TSP-D​​ model for truck-drone coordinated delivery, proposing ​​route-first-cluster-second heuristics​​ to minimize last-mile costs.
+Their work demonstrate ​​substantial savings​​ over truck-only systems.
+Ha et al.'s "On the min-cost Traveling Salesman Problem with Drone" (\cite{WOS:000442591800013}) introduces a ​​cost-centric TSP-D variant​​, proposing ​​a Greedy Randomized Adaptive Search Procedure (GRASP) heuristics​​ to minimize operational expenses, including vehicle wait times.
+Zeng et al.'s "From high-touch to high-tech: COVID-19 drives robotics adoption" (\cite{WOS:000534121800001}) documents how the pandemic accelerated drone deployment for ​​contactless logistics​​, particularly in healthcare and tourism.
+The study forecasts a ​​permanent shift​​ toward hybrid human-robot workflows, despite ethical debates on job displacement.
+​​Wang et al.'s "The vehicle routing problem with drones: several worst-case results" (\cite{WOS:000400384200003}) establishes ​​theoretical bounds​​ for truck-drone coordinated efficiency, proving that drone speed and fleet size dictate maximum time savings.
+Stolaroff et al.'s "Energy use and life cycle greenhouse gas emissions of drones for commercial package delivery" (\cite{WOS:000424872000001}) employs ​​lifecycle assessment (LCA)​​ for drone-based delivery, revealing that small drones exhibit ​​lower per-package energy consumption​​ than ground vehicles for short-haul trips.
+However, the study cautions that expanded ​​warehouse networks and ​​longer flight paths can offset these gains.
+Their findings conclude that, ​​with optimized infrastructure and drone size​​, drone delivery systems hold potential to reduce greenhouse gas emissions compared to conventional logistics.Wang & Sheu's "Vehicle routing problem with drones" (\cite{WOS:000465060600016}) introduces a ​​mixed-integer programming model​​ for the ​​vehicle routing problem with drones (VRPD)​​, extending classical capacitated VRP to accommodate dynamic drone redeployment across trucks.
+Their ​​branch-and-price algorithm​​ optimizes integrated truck-drone routing under flying range and payload constraints, with ​​extensive experiments on practically generated instances​​ demonstrating the algorithm’s ​​robust computational performance​​.
 

### 2025-05-14 latex/draft.tex
更新论文

@@
 (\cite{WOS:001366904300001})) employ bibliometrics to reveal that UAVs are increasingly used over traditional forest inventories to efficiently assess variables like tree height, DBH, biomass, and canopy area through high-resolution sensors.
-While prior bibliometric reviews like "Analyzing Forklift and Drone Applications in Sustainable Logistics" (\cite{WOS:001329532200078})) provide initial insights into drone logistics, their broad scope—spanning both forklifts and drones—and exclusive focus on sustainability limit granular analysis of drone-specific logistics.
+While prior bibliometric reviews like "Analyzing Forklift and Drone Applications in Sustainable Logistics" (\cite{WOS:001329532200078}) provide initial insights into drone logistics, their broad scope—spanning both forklifts and drones—and exclusive focus on sustainability limit granular analysis of drone-specific logistics.
 In addition, this study remains confined to quantitative metrics, without in-depth review of the literature.
@@
 Kevin Dorling, Jordan Heinrichs, Jordan Messier, and Sebastian Magierowski advanced drone routing by developing multi-trip VRPs that optimize energy consumption models (payload/battery weight) and enable drone reuse.
-Their work introduced mixed-integer programs and simulated annealing heuristics, revealing inverse exponential cost-time tradeoffs and offering tools to balance delivery efficiency and budget constraints (\cite{WOS:000623397300001}).
+Their work introduced mixed-integer programs and simulated annealing heuristics, revealing inverse exponential cost-time tradeoffs and offering tools to balance delivery efficiency and budget constraints (\cite{WOS:000391480400007}).
 While individual contributions remain pivotal, several highly cited scholars in drone logistics have achieved prominence through collaborative partnerships.
@@
 \subsection{Citation analysis}
-Our analysis of the most highly cited drone logistics literature begins with the ​​top two papers​​—Murray et al.'s "The flying sidekick traveling salesman problem: Optimization of drone-assisted parcel delivery" (\cite{WOS:000353871700006}) and Dorling et al.'s "Vehicle Routing Problems for Drone Delivery" (\cite{WOS:000623397300001})—both previously detailed in discussions of their authors' contributions.
-Moving to next highly cited works: ​​Menouar et al.'s "UAV-Enabled Intelligent Transportation Systems for the Smart City: Applications and Challenges" (\cite{WOS:000398037700003}) maps UAV applications in urban mobility, identifying key challenges like airspace regulation and cybersecurity for smart-city integration.
-​​Büyüközkan & Gocer's "Digital Supply Chain: Literature review and a proposed framework for future research" (\cite{WOS:000432504700016}) frames drones as a pillar of digitized supply chains, emphasizing their role in agility and IoT-driven automation.
-Agatz et al.'s "Optimization Approaches for the Traveling Salesman Problem with Drone" (\cite{WOS:000442591800013})​​ formalizes the ​​TSP-D​​ model for truck-drone coordinated delivery, proposing ​​route-first-cluster-second heuristics​​ to minimize last-mile costs.
-Their work demonstrate ​​substantial savings​​ over truck-only systems.
-Ha et al.'s "On the min-cost Traveling Salesman Problem with Drone" (\cite{WOS:000442591800013}) introduces a ​​cost-centric TSP-D variant​​, proposing ​​a Greedy Randomized Adaptive Search Procedure (GRASP) heuristics​​ to minimize operational expenses, including vehicle wait times.
-Zeng et al.'s "From high-touch to high-tech: COVID-19 drives robotics adoption" (\cite{WOS:000534121800001}) documents how the pandemic accelerated drone deployment for ​​contactless logistics​​, particularly in healthcare and tourism.
-The study forecasts a ​​permanent shift​​ toward hybrid human-robot workflows, despite ethical debates on job displacement.
-​​Wang et al.'s "The vehicle routing problem with drones: several worst-case results" (\cite{WOS:000400384200003}) establishes ​​theoretical bounds​​ for truck-drone coordinated efficiency, proving that drone speed and fleet size dictate maximum time savings.
-Stolaroff et al.'s "Energy use and life cycle greenhouse gas emissions of drones for commercial package delivery" (\cite{WOS:000424872000001}) employs ​​lifecycle assessment (LCA)​​ for drone-based delivery, revealing that small drones exhibit ​​lower per-package energy consumption​​ than ground vehicles for short-haul trips.
-However, the study cautions that expanded ​​warehouse networks and ​​longer flight paths can offset these gains.
-Their findings conclude that, ​​with optimized infrastructure and drone size​​, drone delivery systems hold potential to reduce greenhouse gas emissions compared to conventional logistics.Wang & Sheu's "Vehicle routing problem with drones" (\cite{WOS:000465060600016}) introduces a ​​mixed-integer programming model​​ for the ​​vehicle routing problem with drones (VRPD)​​, extending classical capacitated VRP to accommodate dynamic drone redeployment across trucks.
-Their ​​branch-and-price algorithm​​ optimizes integrated truck-drone routing under flying range and payload constraints, with ​​extensive experiments on practically generated instances​​ demonstrating the algorithm’s ​​robust computational performance​​.
+Our analysis of the most highly cited drone logistics literature begins with the top two papers—Murray et al.'s "The flying sidekick traveling salesman problem: Optimization of drone-assisted parcel delivery" (\cite{WOS:000353871700006}) and Dorling et al.'s "Vehicle Routing Problems for Drone Delivery" (\cite{WOS:000391480400007})—both previously detailed in discussions of their authors' contributions.
+Moving to next highly cited works: Menouar et al.'s "UAV-Enabled Intelligent Transportation Systems for the Smart City: Applications and Challenges" (\cite{WOS:000398037700003}) maps UAV applications in urban mobility, identifying key challenges like airspace regulation and cybersecurity for smart-city integration.
+Büyüközkan \& Gocer's "Digital Supply Chain: Literature review and a proposed framework for future research" (\cite{WOS:000432504700016}) frames drones as a pillar of digitized supply chains, emphasizing their role in agility and IoT-driven automation.
+Agatz et al.'s "Optimization Approaches for the Traveling Salesman Problem with Drone" (\cite{WOS:000442591800013}) formalizes the TSP-D model for truck-drone coordinated delivery, proposing route-first-cluster-second heuristics to minimize last-mile costs.
+Their work demonstrate substantial savings over truck-only systems.
+Ha et al.'s "On the min-cost Traveling Salesman Problem with Drone" (\cite{WOS:000442591800013}) introduces a cost-centric TSP-D variant, proposing a Greedy Randomized Adaptive Search Procedure (GRASP) heuristics to minimize operational expenses, including vehicle wait times.
+Zeng et al.'s "From high-touch to high-tech: COVID-19 drives robotics adoption" (\cite{WOS:000534121800001}) documents how the pandemic accelerated drone deployment for contactless logistics, particularly in healthcare and tourism.
+The study forecasts a permanent shift toward hybrid human-robot workflows, despite ethical debates on job displacement.
+Wang et al.'s "The vehicle routing problem with drones: several worst-case results" (\cite{WOS:000400384200003}) establishes theoretical bounds for truck-drone coordinated efficiency, proving that drone speed and fleet size dictate maximum time savings.
+Stolaroff et al.'s "Energy use and life cycle greenhouse gas emissions of drones for commercial package delivery" (\cite{WOS:000424872000001}) employs lifecycle assessment (LCA) for drone-based delivery, revealing that small drones exhibit lower per-package energy consumption than ground vehicles for short-haul trips.
+However, the study cautions that expanded warehouse networks and longer flight paths can offset these gains.
+Their findings conclude that, with optimized infrastructure and drone size, drone delivery systems hold potential to reduce greenhouse gas emissions compared to conventional logistics.Wang \& Sheu's "Vehicle routing problem with drones" (\cite{WOS:000465060600016}) introduces a mixed-integer programming model for the vehicle routing problem with drones (VRPD), extending classical capacitated VRP to accommodate dynamic drone redeployment across trucks.
+Their branch-and-price algorithm optimizes integrated truck-drone routing under flying range and payload constraints, with extensive experiments on practically generated instances demonstrating the algorithm’s robust computational performance.
+
+\subsection{Countries}
+The analysis of national contributions to drone logistics research reveals a clear hierarchy in drone logistics research contributions across countries, measured by publication volume, citation impact, and H-index.
+The ​​United States​​ leads in citation impact (13,612 citations) and H-index (56), despite ranking second in publication count (384 studies), underscoring its dominant role in high-impact research.
+​​China​​ ranks first in publication volume (528 studies) but second in citations (8,437) and H-index (45), reflecting a large-scale output with relatively lower per-study impact compared to the U.S.
+​​South Korea​​ holds third place across all metrics (138 publications, 4,493 citations, H-index 36), demonstrating balanced productivity and impact.
+
+European nations like Germany and Italy (83 publications each) achieve identical H-indices (27), demonstrating comparable scholarly influence at a moderate output level.
+​​Canada​​ (75 publications, H-index 23) and ​​Australia​​ (72 publications, H-index 24) exhibit efficient research ecosystems with mid-tier citation traction (2,898 and 1,915 citations, respectively).
+​​India​​ and ​​Saudi Arabia​​, while emerging as active contributors (110 and 55 publications), show lower H-indices (21 and unlisted), indicating room for greater global impact.
+
+\subsection{Institutions}
+In this section, we turn to analyzing high-impact institutions in drone logistics research.​​ ​​Sejong University​​ emerges as a leading institution with ​​1,712 total citations​​ and an ​​H-index of 19​​, driven by interdisciplinary collaborations.
+While most of its top-cited works focus on ​​consumer behavior and technology adoption​​ in drone food delivery (e.g., perceived innovativeness (\cite{WOS:000478712400012}), risk perception (\cite{WOS:000495004400013}), and COVID-19 impacts (\cite{WOS:000605628800016}))—led by ​​Jinsoo Hwang​​’s aforementioned behavioral science studies—its most cited paper, "Routing in Flying Ad Hoc Networks: A Comprehensive Survey" (218 citations), represents a distinct technical domain.This survey systematically categorizes routing protocols for ​​Flying Ad Hoc Networks (FANETs)​​, analyzing their strengths/weaknesses against challenges like high mobility and topology instability.
+It evaluates protocols using mobility models and proposes a taxonomy to guide future FANET communication design (\cite{WOS:000538038400010})​​.
+The institution’s research portfolio underscores a balanced emphasis on ​​technical and ​​socioeconomic research, positioning it as a hub for drone logistics innovation.
+Auburn University​​ holds a notable position in drone logistics research with ​​1,062 total citations​​, though its influence is overwhelmingly driven by a single landmark study: "The flying sidekick traveling salesman problem" (920 citations) (\cite{WOS:000353871700006}).
+​​Purdue University's research in drone logistics spans optimization frameworks​​—mathematical models like insertion heuristics that handle large-scale routing across hundreds of nodes (\cite{WOS:000460496000002})—and ​​real-world constraint modeling​​, which integrates operational hurdles such as battery limits (\cite{WOS:000532795300023}), No-Fly Zones (\cite{WOS:000474324300017}), and multi-trip payload fluctuations (\cite{WOS:000523602300006}).
+University of Maryland has ​​947 total citations​​.
+Its foundational work, "The vehicle routing problem with drones: several worst-case results" (\cite{WOS:000400384200003})  (325 citations), quantified the maximum time savings achievable via drones under varying speed ratios and fleet sizes.
+A follow-up study  (229 citations) by the same institution expanded the previous study by linking it to ​​Amdahl’s Law​​, emphasizing how drones enhance efficiency via ​​parallel task execution (\cite{WOS:000404719400004})​​.
+​​York University (Canada) and University of Calgary's influence in drone logistics are heavily anchored by a single landmark study: "Vehicle Routing Problems for Drone Delivery" (\cite{WOS:000391480400007}).
+Authored by Dorling et al., this work established ​​energy-aware multitrip routing models​​, integrating linear payload-battery energy consumption into MILP formulations and simulated annealing heuristics.
+The University of Florida's impact in drone logistics is dominated by "UAV-Enabled Intelligent Transportation Systems for the Smart City: Applications and Challenges" (\cite{WOS:000398037700003}) (609 citations, ~74\% of total citations).
+This study ​​maps UAV applications and ​​key challenges for smart-city intelligent transportation systems.
+State University of New York​​ has advanced drone logistics with ​​798 citations, focusing on ​​multi-drone coordinated delivery​​ (\cite{WOS:000509790500020}) and ​​barrier analysis (\cite{WOS:000547773000001})​​.
+
+The interplay between publication volume, H-index, and total citations reveals distinct institutional research profiles in drone logistics.
+​​Sejong University​​ exemplifies balanced excellence, ranking ​​4th in output​​ (27 papers) but ​​1st in both H-index (19) and total citations (1,712)​​, underscoring its dual strength in behavioral studies (\cite{WOS:000478712400012}) and technical innovations (\cite{WOS:000538038400010}).
+In contrast, ​​Hong Kong Polytechnic University​​ leads in sheer output (42 papers) but trails in H-index (14) and total citations (absent from the top 10), reflecting a high-volume yet moderately cited portfolio.
+Chinese institutions like ​​Nanjing University of Aeronautics & Astronautics​​ (2nd in output, 33 papers) and ​​Beihang University​​ (3rd, 28 papers) prioritize quantity but lack representation in H-index and citation rankings.
+Nanyang Technological University​​ (6th in output, 22 papers; 3rd in H-index, 13) and ​​University of New South Wales Sydney​​ (3rd in H-index, 13) achieve higher per-paper impact through optimization frameworks​​ (\cite{WOS:000501349900060}) and ​​collaborative delivery models​​ (\cite{WOS:000467564700204}).
+Tsinghua University (8th in output, 20 papers; 8th in H-index, 10), Purdue University (9th in output, 19 papers; 8th in H-index, 10) and the University of Maryland (9th in output, 19 papers; 8th in H-index, 10) demonstrate moderate yet consistent influence across output and impact metrics.
 

### 2025-05-14 institutions.py

@@ -1,0 +1,244 @@
+import re
+from collections import defaultdict
+
+# ================== 用户配置区域 ==================
+INSTITUTION_MAPPING = {
+    "Purdue University System": "Purdue University",
+    "Auburn University System": "Auburn University",
+    "University System of Maryland": "University of Maryland",
+    "University of Maryland College Park": "University of Maryland",
+    "Erasmus University Rotterdam - Excl Erasmus MC": "Erasmus University Rotterdam",
+}
+
+EXCLUDE_INSTITUTIONS = set()
+OUTPUT_FILE = "institution_rankings.txt"
+
+
+# ================== 数据处理函数 ==================
+def clean_institution_name(raw_name):
+    """机构名称标准化处理"""
+    name = raw_name.strip()
+
+    # 应用名称映射
+    for old, new in INSTITUTION_MAPPING.items():
+        if name.lower() == old.lower():
+            return new
+
+    # 去除系统后缀
+    name = re.sub(r',.*?(System|Campus)\b', '', name, flags=re.IGNORECASE)
+
+    # 统一缩写
+    name = re.sub(r'\bUniv\b', 'University', name, flags=re.IGNORECASE)
+
+    return name
+
+
+def parse_records(file_path):
+    """解析WOS文件结构"""
+    records = []
+    current_record = []
+    in_record = False
+
+    with open(file_path, 'r', encoding='utf-8') as f:
+        for line in f:
+            line = line.rstrip('\n')
+
+            if re.match(r'^PT\s', line):
+                if in_record:
+                    records.append(current_record)
+                current_record = [line]
+                in_record = True
+            elif in_record and line == 'ER':
+                current_record.append(line)
+                records.append(current_record)
+                current_record = []
+                in_record = False
+            elif in_record:
+                current_record.append(line)
+
+    return records
+
+
+def parse_record(record_lines):
+    """解析单条记录数据"""
+    data = defaultdict(list)
+    current_field = None
+
+    for line in record_lines:
+        if re.match(r'^[A-Z]{1,2}\d?\s', line[:3]):
+            field_code = line[:2]
+            content = line[3:].strip()
+            current_field = field_code
+            data[field_code].append(content)
+        elif current_field:
+            data[current_field][-1] += ' ' + line.strip()
+
+    # 处理机构信息
+    institutions = set()
[…]

### 2025-05-15 calculate_by_source.py
保存代码

@@ -1,44 +1,148 @@
 from collections import defaultdict
 
-# 读取文件
-with open('data/data.txt', 'r', encoding='utf-8') as file:
-    lines = file.readlines()
 
-# 初始化统计变量
-journal_count = defaultdict(int)  # 期刊发文数量
-journal_citations = defaultdict(int)  # 期刊总被引次数
-current_journal = None  # 当前文献的期刊名称
-current_citations = 0  # 当前文献的被引次数
 
-for line in lines:
-    # 提取期刊名称
-    if line.startswith('SO'):
-        current_journal = line.strip().split('SO ')[-1].strip()
-    # 提取被引次数
-    elif line.startswith('TC'):
-        current_citations = int(line.strip().split()[-1])
-        # 更新期刊统计
-        if current_journal:
-            journal_count[current_journal] += 1
-            journal_citations[current_journal] += current_citations
 
-# 计算各期刊的平均被引次数
-journal_avg_citations = {
-    journal: journal_citations[journal] / journal_count[journal]
-    for journal in journal_count
-}
+def analyze_journals(file_path):
+    """执行期刊分析"""
+    journal_data = defaultdict(lambda: {
+        'count': 0,
+        'total_citations': 0,
+        'articles': []
+    })
 
-# 按发文数量排序
-sorted_journals_by_count = sorted(journal_count.items(), key=lambda x: x[1], reverse=True)
-# 按平均被引次数排序
-sorted_journals_by_avg_citations = sorted(journal_avg_citations.items(), key=lambda x: x[1], reverse=True)
+    # 处理每条文献记录
+    for record in parse_wos_records(file_path):
+        journal = record['journal']
+        journal_data[journal]['count'] += 1
+        journal_data[journal]['total_citations'] += record['citations']
 
-# 输出高频期刊（按发文数量）
-print("高频期刊统计（按发文数量）：")
-for journal, count in sorted_journals_by_count[:20]:  # 输出前20个
-    print(f"{journal}: 发文数量 {count} 次，平均被引次数 {journal_avg_citations[journal]:.2f} 次")
+        # 存储文章详细信息（限制存储字段）
+        journal_data[journal]['articles'].append({
+            'citations': record['citations'],
+            'title': record['title'],
+            'authors': record['authors'][:3] + ['...'] if len(record['authors']) > 3 else record['authors'],
[…]

### 2025-05-15 calculate_by_year.py

@@ -17,7 +17,10 @@ for line in lines:
 sorted_years = sorted(year_count.keys())
 counts = [year_count[year] for year in sorted_years]
 
-print(counts)
+# 打印年份及对应数量（新增部分）
+print("Year : Publications")
+for year, count in zip(sorted_years, counts):
+    print(f"{year} : {count}")
 
 # 绘制柱状图
 plt.figure(figsize=(10, 6))

### 2025-05-15 high_cited_articles.py

@@ -31,21 +31,28 @@ def parse_records(file_path):
 
 
 def parse_record_fields(record_lines):
-    """解析单条记录的字段内容"""
-    data = {'TI': '', 'PY': 0, 'TC': 0}
+    """解析单条记录的字段内容（新增摘要和作者解析）"""
+    data = {'TI': '', 'PY': 0, 'TC': 0, 'AB': '', 'AU': []}
     current_field = None
 
     for line in record_lines:
-        # 检测字段标识（如TI/PY/TC）
+        # 检测字段标识（如TI/AB/AU等）
         if re.match(r'^[A-Z]{1,2}\d?\s', line[:3]):
             field_code = line[:2]
             content = line[3:].strip()
             current_field = field_code
-            if field_code in data:
+
+            if field_code == 'AU':
+                data['AU'].append(content)
+            elif field_code in data:
                 data[field_code] = content
-        # 处理多行字段的延续内容
-        elif current_field in data:
-            data[current_field] += ' ' + line.strip()
+        else:
+            # 处理多行字段的延续内容
+            stripped_line = line.strip()
+            if current_field == 'AU' and data['AU']:
+                data['AU'][-1] += ' ' + stripped_line
+            elif current_field in data:
+                data[current_field] += ' ' + stripped_line
 
     # 数据类型转换
     try:
@@ -59,7 +66,9 @@ def parse_record_fields(record_lines):
         data['TC'] = 0
 
     return {
-        'title': data['TI'],
+        'title': data['TI'].strip(),
+        'abstract': data['AB'].strip(),
+        'authors': '; '.join(data['AU']),
         'year': data['PY'],
         'citations': data['TC']
     }
@@ -75,12 +84,20 @@ if __name__ == '__main__':
     for rec in records:
         parsed = parse_record_fields(rec)
         if parsed['year'] >= 2000 and parsed['citations'] > 0:
-            high_cited.append((parsed['title'], parsed['citations']))
+            high_cited.append((
+                parsed['title'],
+                parsed['abstract'],
+                parsed['authors'],
+                parsed['citations']
+            ))
 
     # 按被引次数降序排序
-    high_cited_sorted = sorted(high_cited, key=lambda x: (-x[1], x[0]))[0:500]
+    high_cited_sorted = sorted(high_cited, key=lambda x: (-x[3], x[0]))[:20]
 
-    # 打印结果
[…]

### 2025-05-15 high_cited_authors_with_papers.py

@@ -1,0 +1,98 @@
+import re
+from collections import defaultdict
+
+# 定义正则表达式匹配字段标识符
+field_pattern = re.compile(r'^([A-Z]{2})\s*(.*)')  # 允许字段代码前有空格（处理后）
+
+articles = []
+current_article = None
+current_field = None
+
+with open('data/data.txt', 'r', encoding='utf-8') as file:
+    for line in file:
+        # 清除特殊字符和格式
+        line = line.encode('utf-8').replace(b'\xef\xbb\xbf', b'').decode('utf-8')  # 处理BOM
+        line = line.lstrip('\ufeff')  # 去除零宽度非断开空格
+        line = line.rstrip('\n')  # 去除换行符
+
+        # 检测新文章开始（PT J）
+        if line.startswith('PT J'):
+            if current_article:
+                articles.append(current_article)
+            current_article = {
+                'authors': [],
+                'title': '',
+                'abstract': '',
+                'citations': 0
+            }
+            current_field = None
+            continue
+
+        # 解析字段内容（增强鲁棒性）
+        if len(line) >= 2:
+            # 处理带缩进的续行（如作者/标题/摘要多行情况）
+            if current_field and (line.startswith('   ') or not line.strip()):
+                content = line.strip()
+                if current_field == 'AU':
+                    current_article['authors'].append(content)
+                elif current_field == 'TI':
+                    current_article['title'] += ' ' + content
+                elif current_field == 'AB':
+                    current_article['abstract'] += ' ' + content
+                continue
+
+            # 处理新字段
+            match = field_pattern.match(line)
+            if match:
+                field_code, content = match.groups()
+                current_field = field_code
+                content = content.strip()
+
+                if field_code == 'AU':
+                    current_article['authors'].append(content)
+                elif field_code == 'TI':
+                    current_article['title'] = content
+                elif field_code == 'AB':
+                    current_article['abstract'] = content
+                elif field_code == 'TC':
+                    current_article['citations'] = int(content)
+
+    # 添加最后一篇文章
+    if current_article:
+        articles.append(current_article)
+
+import re
+from collections import defaultdict
+
+# ... [前面的解析代码保持不变，直到构建作者数据库] ...
+
+# 构建作者数据库（添加引用次数存储）
[…]

### 2025-05-15 high_freq_country.py

@@ -1,95 +1,136 @@
-from collections import defaultdict, Counter
+import json
+import re
+from collections import defaultdict
+
 import re
 
-# 读取文件
-with open('data/data.txt', 'r', encoding='utf-8') as file:
-    lines = file.readlines()
 
-# 统计国家和被引国家
-country_count = defaultdict(int)  # 国家出现次数
-country_citation_count = defaultdict(int)  # 国家被引次数
-country_citation_list = defaultdict(list)  # 存储每个国家的被引次数列表（用于计算 H 指数）
-current_countries = []
-current_citations = 0
-is_c1 = False  # 标记是否正在读取 C1 字段
-current_c1_lines = []  # 存储当前 C1 字段的多行内容
+def extract_country_v2(address_line):
+    """增强版国家提取函数"""
+    # 移除作者信息
+    if '] ' in address_line:
+        _, address_part = address_line.split('] ', 1)
+    else:
+        address_part = address_line
 
-# 正则表达式匹配两个大写字母和一个空格或制表符开头的行
-field_pattern = re.compile(r'^[A-Z]{2}[ \t]')
-# 正则表达式匹配一个字母和一个数字开头的行（如 C2）
-c2_pattern = re.compile(r'^[A-Z][0-9]')
-
-# 提取国家的函数
-def extract_country(address):
-    # 去掉最后的句号
-    address = address.rstrip('.')
-    # 提取最后一段
-    last_part = address.split(',')[-1].strip()
-    # 如果最后一段包含 USA，则单独提取 USA
-    if 'USA' in last_part:
+    # 处理美国地址的特殊情况
+    usa_match = re.search(r',\s*([^,]*USA)\s*\.?$', address_part, re.IGNORECASE)
+    if usa_match:
         return 'USA'
-    return last_part
 
-# 计算 H 指数的函数
-def calculate_h_index(citation_list):
-    # 将被引次数从高到低排序
-    sorted_citations = sorted(citation_list, reverse=True)
-    # 计算 H 指数
-    h_index = 0
-    for i, citations in enumerate(sorted_citations):
-        if citations >= i + 1:
-            h_index = i + 1
+    # 通用处理逻辑
+    parts = [p.strip() for p in address_part.split(',')]
+    for part in reversed(parts):
+        clean_part = part.rstrip('.').strip()
+        if clean_part:
+            return clean_part
+    return "Unknown"
+
+
+def process_countries_v2(c1_data):
+    """处理多行C1数据"""
+    countries = set()
+
+    # 统一处理为列表
[…]

### 2025-05-15 high_freq_keywords.py

@@ -6,7 +6,7 @@ synonyms = {
     "Unmanned aerial vehicle": ["uav", "uavs", "unmanned aerial vehicles",
                                 "unmanned aerial vehicles (uav)", "unmanned aerial vehicle (uav)", "uas",
                                 "unmanned aerial vehicle", "autonomous aerial vehicles"],
-    "drone": ["Drone", "drones"],
+    "Drone": ["drone", "drones"],
     "Traveling salesman problem": ["tsp", "traveling salesperson problem"],
     "Vehicle routing problem": ["vrp", "vehicle route problem"],
     "Optimization": ["optimisation", "optimalization"],  # 英式和美式拼写
@@ -39,7 +39,7 @@ for line in lines:
             keyword_count[standardized_keyword] += 1
 
 # 获取高频关键词（例如前10个）
-top_keywords = Counter(keyword_count).most_common(50)
+top_keywords = Counter(keyword_count).most_common(20)
 
 # 输出高频关键词
 print("高频关键词统计：")

### 2025-05-15 high_freq_keywords_split.py

@@ -3,7 +3,7 @@ from collections import defaultdict, Counter
 # 手工填入同义词映射表
 # 格式：标准词: [同义词1, 同义词2, ...]
 synonyms = {
-    "Unmanned aerial vehicle": ["uav", "drone", "drones", "uavs", "unmanned aerial vehicles",
+    "Drone": ["uav", "Unmanned aerial vehicle", "drone", "drones", "uavs", "unmanned aerial vehicles",
                                 "unmanned aerial vehicles (uav)", "unmanned aerial vehicle (uav)", "uas",
                                 "unmanned aerial vehicle", "autonomous aerial vehicles"],
     "Traveling salesman problem": ["tsp", "traveling salesperson problem"],
@@ -50,8 +50,8 @@ for line in lines:
                     keyword_count_after_2015[standardized_keyword] += 1
 
 # 获取高频关键词（例如前20个）
-top_keywords_before_2015 = Counter(keyword_count_before_2015).most_common(15)
-top_keywords_after_2015 = Counter(keyword_count_after_2015).most_common(15)
+top_keywords_before_2015 = Counter(keyword_count_before_2015).most_common(10)
+top_keywords_after_2015 = Counter(keyword_count_after_2015).most_common(10)
 
 print("2020 年前高频关键词统计：")
 for keyword, count in top_keywords_before_2015:

### 2025-05-15 highly_cited_institutions.py

@@ -1,0 +1,176 @@
+import re
+from collections import defaultdict
+
+# ================== 用户配置区域 ==================
+# 机构名称标准化映射表（旧名称 -> 新名称）
+INSTITUTION_MAPPING = {
+    "Purdue University System": "Purdue University",
+    "Auburn University System": "Auburn University",
+    "University of Maryland College Park": "University of Maryland",
+    "Erasmus University Rotterdam - Excl Erasmus MC": "Erasmus University Rotterdam",
+    # 示例格式："旧名称": "标准名称"
+}
+
+# 需要完全排除的机构列表（全大写）
+EXCLUDE_INSTITUTIONS = {
+    # 示例："OBSOLETE INSTITUTION"
+}
+
+
+# ================== 数据处理函数 ==================
+def clean_institution_name(raw_name):
+    """机构名称清洗"""
+    name = raw_name.strip()
+
+    # 应用名称映射
+    for old, new in INSTITUTION_MAPPING.items():
+        if name.lower() == old.lower():
+            return new
+
+    # 去除系统后缀
+    name = re.sub(r',.*?(System|Campus)\b', '', name, flags=re.IGNORECASE)
+
+    # 统一缩写
+    name = re.sub(r'\bUniv\b', 'University', name, flags=re.IGNORECASE)
+
+    return name
+
+
+def parse_records(file_path):
+    """解析WOS文件"""
+    records = []
+    current_record = []
+    in_record = False
+
+    with open(file_path, 'r', encoding='utf-8') as f:
+        for line in f:
+            line = line.rstrip('\n')
+
+            if re.match(r'^PT\s', line):
+                if in_record:
+                    records.append(current_record)
+                current_record = [line]
+                in_record = True
+            elif in_record and line == 'ER':
+                current_record.append(line)
+                records.append(current_record)
+                current_record = []
+                in_record = False
+            elif in_record:
+                current_record.append(line)
+
+    return records
+
+
+def parse_record(record_lines):
+    """解析单条记录"""
+    data = defaultdict(list)
+    current_field = None
+
+    for line in record_lines:
+        # 检测字段开始
+        if re.match(r'^[A-Z]{1,2}\d?\s', line[:3]):
+            field_code = line[:2]
+            content = line[3:].strip()
+            current_field = field_code
+            data[field_code].append(content)
+        else:
+            # 处理续行内容
+            if current_field:
+                stripped = line.strip()
[…]

### 2025-05-15 temp.py

@@ -1,48 +1,49 @@
 import json
+import re
+from collections import defaultdict
 
-def extract_true_tis(jsonl_file):
-    true_tis = set()
-    with open(jsonl_file, 'r', encoding='utf-8') as f:
-        for line in f:
-            data = json.loads(line)
-            if data['status'] == 'success':
-                for response in data['response']:
-                    if response['label'] == 'true':
-                        true_tis.add(data['original_data']['TI'].strip())
-    return true_tis
 
-def filter_and_write_records(data_file, output_file, true_tis):
-    with open(data_file, 'r', encoding='utf-8') as f_in, \
-         open(output_file, 'w', encoding='utf-8') as f_out:
-        current_record = []
-        current_ti = None
-        in_ti = False
-        for line in f_in:
-            if line.startswith('ER'):
-                # 检查当前记录的TI是否匹配
-                if current_ti and current_ti in true_tis:
-                    f_out.write(''.join(current_record))
-                    f_out.write(line)
-                current_record = []
-                current_ti = None
-                in_ti = False
-            else:
-                current_record.append(line)
-                # 处理TI字段
-                if line.startswith('TI '):
-                    current_ti = line[3:].strip()
-                    in_ti = True
-                elif in_ti and line.startswith('   '):  # 多行TI的缩进部分
-                    current_ti += ' ' + line.strip()
+def wos_to_jsonl(input_path, output_path):
+    """流式处理WOS文件，直接生成JSONL"""
+    field_start = re.compile(r'^([A-Z]{2}|[A-Z]\d)\s(.*)')
+    current_record = defaultdict(list)
+    current_field = None
+
+    with open(input_path, 'r', encoding='utf-8-sig') as fin, \
+            open(output_path, 'w', encoding='utf-8') as fout:
+
+        for line in fin:
+            line = line.rstrip('\n').lstrip('\ufeff').rstrip('\r')
+
+            # 处理记录结束
+            if line == 'ER':
+                if current_record:
+                    # 转换值为字符串或列表
+                    record = {
+                        k: v[0] if len(v) == 1 else v
+                        for k, v in current_record.items()
+                    }
+                    fout.write(json.dumps(record, ensure_ascii=False) + '\n')
+                    current_record = defaultdict(list)
+                current_field = None
+                continue
+
+            # 字段开始检测
+            if match := field_start.match(line):
+                current_field = match.group(1)
[…]

### 2025-05-15 latex/draft.tex
更新论文

@@
 \addbibresource{references.bib} % 确保你的.bib文件名称正确
+\usepackage{graphicx}
+\usepackage{booktabs} % 专业表格宏包
+\usepackage{array}    % 增强表格对齐
+\usepackage{tabularx} % 可选：适应文本宽度
+\usepackage{placeins} % 在导言区添加
+\usepackage{ragged2e}  % 文本对齐优化
+
+\usepackage{threeparttable} % 表格注释支持
+\newcolumntype{Y}{>{\RaggedRight\arraybackslash}X} % 自适应左对齐列
+
+\usepackage{multirow} % 合并单元格（用于处理并列排名）
+
+\graphicspath{{images/}} % 指定图片路径
 
@@
 
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=\textwidth, keepaspectratio]{images/Figure_1}
+  \caption{Number of publications per year}
+  \label{fig:Figure}
+\end{figure}
+
 \subsection{Keywords}
@@
 This keyword distribution pattern shows delivery applications exhibit fewer distinct high-frequency descriptors compared to platform technologies and navigation algorithms, where drone (347), unmanned aerial vehicle (316), routing (90), and their derivative terms form a denser lexical network.
+
+\begin{table}[htbp]
+  \centering
+  \caption{High-frequency Keywords in Drone Logistics Research}
+  \label{tab:keyword_frequency}
+  \begin{tabular}{@{} l r @{}} % 左对齐关键词，右对齐频率
+    \toprule
+    \textbf{Keyword} & \textbf{Frequency} \\
+    \midrule
+    Drone & 347 \\
+    Unmanned aerial vehicle & 316 \\
+    Routing & 90 \\
+    Logistics & 80 \\
+    Drone delivery & 79 \\
+    Path planning & 57 \\
+    Last-mile delivery & 50 \\
+    Optimization & 43 \\
+    Vehicle routing & 39 \\
+    Delivery & 31 \\
+    Transportation & 31 \\
+    Covid-19 & 30 \\
+    Vehicle routing problem & 27 \\
+    Humanitarian logistics & 25 \\
+    Traveling salesman problem & 24 \\
+    Urban air mobility & 24 \\
+    Parcel delivery & 23 \\
+    Energy consumption & 23 \\
+    Trajectory & 23 \\
+    Task analysis & 21 \\
+    \bottomrule
+  \end{tabular}
+\end{table}
 
@@
 
+\begin{table}[htbp]
+  \centering
+  \caption{Top Cited Authors in Drone Logistics Research}
+  \label{tab:ranked_authors}
+  \begin{tabular}{@{} c l r @{}} % 三列：居中排名，左对齐作者，右对齐引用次数
+    \toprule
+    \textbf{Rank} & \textbf{Author} & \textbf{Citations} \\
+    \midrule
+    1 & Hwang, J & 1434 \\
+    2 & Murray, CC & 1235 \\
+    3 & Chu, AG & 920 \\
+    4 & Poikonen, S & 867 \\
+    5 & Lee, S & 857 \\
+    6 & Kim, JJ & 812 \\
+    7 & Golden, B & 784 \\
+    \multirow{4}{*}{8} & Dorling, K & 766 \\ % 合并排名单元格
+                        & Heinrichs, J & 766 \\
+                        & Messier, GG & 766 \\
+                        & Magierowski, S & 766 \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+\FloatBarrier % 后续内容不会越过此屏障
+
 \subsection{Citation analysis}
@@
 
+\begin{table}[htbp]
+  \centering
+  \caption{Top Cited Articles in Drone Logistics Research (2010-2023)}
+  \label{tab:top_articles}
+  \begin{tabularx}{\textwidth}{@{} >{\centering\arraybackslash}p{1.5cm} X r @{}}
+    \toprule
+    \textbf{Rank} & \textbf{Article Title} & \textbf{Citations} \\
+    \midrule
+    1 & The flying sidekick traveling salesman problem: Optimization of drone-assisted parcel delivery & 920 \\
+    2 & Vehicle Routing Problems for Drone Delivery & 766 \\
+    3 & UAV-Enabled Intelligent Transportation Systems for the Smart City: Applications and Challenges & 609 \\
+    4 & Digital Supply Chain: Literature review and a proposed framework for future research & 579 \\
+    5 & Optimization Approaches for the Traveling Salesman Problem with Drone & 523 \\
+    6 & On the min-cost Traveling Salesman Problem with Drone & 375 \\
+    7 & From high-touch to high-tech: COVID-19 drives robotics adoption & 336 \\
+    8 & The vehicle routing problem with drones: several worst-case results & 325 \\
+    9 & Energy use and life cycle greenhouse gas emissions of drones for commercial package delivery & 316 \\
+    10 & Vehicle routing problem with drones & 311 \\
+    \bottomrule
+  \end{tabularx}
+\end{table}
+
+\FloatBarrier % 后续内容不会越过此屏障
+
 \subsection{Countries}
 The analysis of national contributions to drone logistics research reveals a clear hierarchy in drone logistics research contributions across countries, measured by publication volume, citation impact, and H-index.
-The ​​United States​​ leads in citation impact (13,612 citations) and H-index (56), despite ranking second in publication count (384 studies), underscoring its dominant role in high-impact research.
-​​China​​ ranks first in publication volume (528 studies) but second in citations (8,437) and H-index (45), reflecting a large-scale output with relatively lower per-study impact compared to the U.S.
-​​South Korea​​ holds third place across all metrics (138 publications, 4,493 citations, H-index 36), demonstrating balanced productivity and impact.
+The United States leads in citation impact (13,548 citations) and H-index (56), despite ranking second in publication count (383 studies), underscoring its dominant role in high-impact research.
+China ranks first in publication volume (528 studies) but second in citations (8,437) and H-index (45), reflecting a large-scale output with relatively lower per-study impact compared to the U.S.
+South Korea holds third place across all metrics (138 publications, 4,493 citations, H-index 36), demonstrating balanced productivity and impact.
 
-European nations like Germany and Italy (83 publications each) achieve identical H-indices (27), demonstrating comparable scholarly influence at a moderate output level.
-​​Canada​​ (75 publications, H-index 23) and ​​Australia​​ (72 publications, H-index 24) exhibit efficient research ecosystems with mid-tier citation traction (2,898 and 1,915 citations, respectively).
-​​India​​ and ​​Saudi Arabia​​, while emerging as active contributors (110 and 55 publications), show lower H-indices (21 and unlisted), indicating room for greater global impact.
+European nations like Germany (82 studies) and Italy (83 studies) achieve identical H-indices (27), demonstrating comparable scholarly influence at a moderate output level.
+Canada (75 publications, H-index 23) and Australia (72 publications, H-index 24) exhibit efficient research ecosystems with mid-tier citation traction (2,898 and 1,915 citations, respectively).
+India, while emerging as an active contributor (109 publications), show lower H-indices (21), indicating room for greater global impact.
+
+\begin{table}[htbp]
+  \centering
+  \caption{National Research Output Metrics in Drone Logistics}
+  \label{tab:research_metrics}
+  \begin{tabularx}{0.9\textwidth}{@{} >{\RaggedRight}p{3cm} r r r @{}}
+    \toprule
+    \textbf{Country} & \textbf{Publications} & \textbf{Total Citations} & \textbf{H-index} \\
+    \midrule
+    USA              & 383  & 13548 & 56 \\
+    Peoples R China  & 528  & 8437  & 45 \\
+    South Korea      & 138  & 4493  & 36 \\
+    Germany          & 82   & 2604  & 27 \\
+    Italy            & 83   & 2023  & 27 \\
+    England          & 110  & 1977  & 26 \\
+    Australia        & 72   & 1915  & 24 \\
+    Canada           & 75   & 2898  & 23 \\
+    India            & 109  & 1582  & 21 \\
+    Spain            & 52   & 1388  & 19 \\
+    \bottomrule
+  \end{tabularx}
+\end{table}
 
 \subsection{Institutions}
-In this section, we turn to analyzing high-impact institutions in drone logistics research.​​ ​​Sejong University​​ emerges as a leading institution with ​​1,712 total citations​​ and an ​​H-index of 19​​, driven by interdisciplinary collaborations.
-While most of its top-cited works focus on ​​consumer behavior and technology adoption​​ in drone food delivery (e.g., perceived innovativeness (\cite{WOS:000478712400012}), risk perception (\cite{WOS:000495004400013}), and COVID-19 impacts (\cite{WOS:000605628800016}))—led by ​​Jinsoo Hwang​​’s aforementioned behavioral science studies—its most cited paper, "Routing in Flying Ad Hoc Networks: A Comprehensive Survey" (218 citations), represents a distinct technical domain.This survey systematically categorizes routing protocols for ​​Flying Ad Hoc Networks (FANETs)​​, analyzing their strengths/weaknesses against challenges like high mobility and topology instability.
-It evaluates protocols using mobility models and proposes a taxonomy to guide future FANET communication design (\cite{WOS:000538038400010})​​.
-The institution’s research portfolio underscores a balanced emphasis on ​​technical and ​​socioeconomic research, positioning it as a hub for drone logistics innovation.
-Auburn University​​ holds a notable position in drone logistics research with ​​1,062 total citations​​, though its influence is overwhelmingly driven by a single landmark study: "The flying sidekick traveling salesman problem" (920 citations) (\cite{WOS:000353871700006}).
-​​Purdue University's research in drone logistics spans optimization frameworks​​—mathematical models like insertion heuristics that handle large-scale routing across hundreds of nodes (\cite{WOS:000460496000002})—and ​​real-world constraint modeling​​, which integrates operational hurdles such as battery limits (\cite{WOS:000532795300023}), No-Fly Zones (\cite{WOS:000474324300017}), and multi-trip payload fluctuations (\cite{WOS:000523602300006}).
-University of Maryland has ​​947 total citations​​.
+In this section, we turn to analyzing high-impact institutions in drone logistics research.
+Sejong University emerges as a leading institution with 1,712 total citations and an H-index of 19, driven by interdisciplinary collaborations.
+While most of its top-cited works focus on consumer behavior and technology adoption in drone food delivery (e.g., perceived innovativeness (\cite{WOS:000478712400012}), risk perception (\cite{WOS:000495004400013}), and COVID-19 impacts (\cite{WOS:000605628800016}))—led by Jinsoo Hwang’s aforementioned behavioral science studies—its most cited paper, "Routing in Flying Ad Hoc Networks: A Comprehensive Survey" (218 citations), represents a distinct technical domain.This survey systematically categorizes routing protocols for Flying Ad Hoc Networks (FANETs), analyzing their strengths/weaknesses against challenges like high mobility and topology instability.
+It evaluates protocols using mobility models and proposes a taxonomy to guide future FANET communication design (\cite{WOS:000538038400010}).
+The institution’s research portfolio underscores a balanced emphasis on technical and socioeconomic research, positioning it as a hub for drone logistics innovation.
+Auburn University holds a notable position in drone logistics research with 1,062 total citations, though its influence is overwhelmingly driven by a single landmark study: "The flying sidekick traveling salesman problem" (920 citations) (\cite{WOS:000353871700006}).
+Purdue University's research in drone logistics spans optimization frameworks—mathematical models like insertion heuristics that handle large-scale routing across hundreds of nodes (\cite{WOS:000460496000002})—and real-world constraint modeling, which integrates operational hurdles such as battery limits (\cite{WOS:000532795300023}), No-Fly Zones (\cite{WOS:000474324300017}), and multi-trip payload fluctuations (\cite{WOS:000523602300006}).
+University of Maryland has 947 total citations.
 Its foundational work, "The vehicle routing problem with drones: several worst-case results" (\cite{WOS:000400384200003})  (325 citations), quantified the maximum time savings achievable via drones under varying speed ratios and fleet sizes.
-A follow-up study  (229 citations) by the same institution expanded the previous study by linking it to ​​Amdahl’s Law​​, emphasizing how drones enhance efficiency via ​​parallel task execution (\cite{WOS:000404719400004})​​.
-​​York University (Canada) and University of Calgary's influence in drone logistics are heavily anchored by a single landmark study: "Vehicle Routing Problems for Drone Delivery" (\cite{WOS:000391480400007}).
-Authored by Dorling et al., this work established ​​energy-aware multitrip routing models​​, integrating linear payload-battery energy consumption into MILP formulations and simulated annealing heuristics.
+A follow-up study  (229 citations) by the same institution expanded the previous study by linking it to Amdahl’s Law, emphasizing how drones enhance efficiency via parallel task execution (\cite{WOS:000404719400004}).
+York University (Canada) and University of Calgary's influence in drone logistics are heavily anchored by a single landmark study: "Vehicle Routing Problems for Drone Delivery" (\cite{WOS:000391480400007}).
+Authored by Dorling et al., this work established energy-aware multitrip routing models, integrating linear payload-battery energy consumption into MILP formulations and simulated annealing heuristics.
 The University of Florida's impact in drone logistics is dominated by "UAV-Enabled Intelligent Transportation Systems for the Smart City: Applications and Challenges" (\cite{WOS:000398037700003}) (609 citations, ~74\% of total citations).
-This study ​​maps UAV applications and ​​key challenges for smart-city intelligent transportation systems.
-State University of New York​​ has advanced drone logistics with ​​798 citations, focusing on ​​multi-drone coordinated delivery​​ (\cite{WOS:000509790500020}) and ​​barrier analysis (\cite{WOS:000547773000001})​​.
+This study maps UAV applications and key challenges for smart-city intelligent transportation systems.
+State University of New York has advanced drone logistics with 798 citations, focusing on multi-drone coordinated delivery (\cite{WOS:000509790500020}) and barrier analysis (\cite{WOS:000547773000001}).
 
 The interplay between publication volume, H-index, and total citations reveals distinct institutional research profiles in drone logistics.
-​​Sejong University​​ exemplifies balanced excellence, ranking ​​4th in output​​ (27 papers) but ​​1st in both H-index (19) and total citations (1,712)​​, underscoring its dual strength in behavioral studies (\cite{WOS:000478712400012}) and technical innovations (\cite{WOS:000538038400010}).
-In contrast, ​​Hong Kong Polytechnic University​​ leads in sheer output (42 papers) but trails in H-index (14) and total citations (absent from the top 10), reflecting a high-volume yet moderately cited portfolio.
-Chinese institutions like ​​Nanjing University of Aeronautics & Astronautics​​ (2nd in output, 33 papers) and ​​Beihang University​​ (3rd, 28 papers) prioritize quantity but lack representation in H-index and citation rankings.
-Nanyang Technological University​​ (6th in output, 22 papers; 3rd in H-index, 13) and ​​University of New South Wales Sydney​​ (3rd in H-index, 13) achieve higher per-paper impact through optimization frameworks​​ (\cite{WOS:000501349900060}) and ​​collaborative delivery models​​ (\cite{WOS:000467564700204}).
+Sejong University exemplifies balanced excellence, ranking 4th in output (27 papers) but 1st in both H-index (19) and total citations (1,712), underscoring its dual strength in behavioral studies (\cite{WOS:000478712400012}) and technical innovations (\cite{WOS:000538038400010}).
+In contrast, Hong Kong Polytechnic University leads in sheer output (42 papers) but trails in H-index (14) and total citations (absent from the top 10), reflecting a high-volume yet moderately cited portfolio.
+Chinese institutions like Nanjing University of Aeronautics \& Astronautics (2nd in output, 33 papers) and Beihang University (3rd, 28 papers) prioritize quantity but lack representation in H-index and citation rankings.
+Nanyang Technological University (6th in output, 22 papers; 3rd in H-index, 13) and University of New South Wales Sydney (3rd in H-index, 13) achieve higher per-paper impact through optimization frameworks (\cite{WOS:000501349900060}) and collaborative delivery models (\cite{WOS:000467564700204}).
 Tsinghua University (8th in output, 20 papers; 8th in H-index, 10), Purdue University (9th in output, 19 papers; 8th in H-index, 10) and the University of Maryland (9th in output, 19 papers; 8th in H-index, 10) demonstrate moderate yet consistent influence across output and impact metrics.
+
+\subsection{Sources}
+The distribution of publications and citation impact across journals reveals distinct patterns in drone logistics research.
+Drones leads in publication volume (98 papers) but has the lowest average citations (7.34) among top-output journals.
+Subsequent examination of highly cited articles in Drones suggests a focus on rapid dissemination of applied or technical studies (\cite{WOS:000682822500001, WOS:000682822500021}).
+SUSTAINABILITY (57 papers, 16.88 avg.
+citations) ranks second in publication volume, reflecting its role in hosting interdisciplinary studies on drone logistics' environmental and societal impacts (\cite{WOS:000531558100214, WOS:000428567100315}).
+IEEE TRANSACTIONS ON INTELLIGENT TRANSPORTATION SYSTEMS (57 papers, 28.40 avg.
+citations) matches SUSTAINABILITY in output but achieves higher citations, indicative of its focus on routing innovations (\cite{WOS:000658360600026}) and UAV integration into adaptive traffic systems (\cite{WOS:000684003100038}).
+TRANSPORTATION RESEARCH PART C-EMERGING TECHNOLOGIES (53 papers) achieves the highest average citations (79.15) in this category, reflecting its prominence in publishing high-impact applied optimization studies (\cite{WOS:000353871700006, WOS:000425566000035}).
+IEEE ACCESS (46 papers, 16.00 avg.
+citations) and APPLIED SCIENCES-BASEL (38 papers, 7.50 avg.
+citations) prioritize rapid dissemination of applied research, with IEEE ACCESS showing marginally higher citation influence due to its engineering-focused scope.
+TRANSPORTATION RESEARCH PART E-LOGISTICS AND TRANSPORTATION REVIEW (36 papers, 34.31 avg.
+citations) publishes strategic analyses of drone logistics' cost-efficiency and supply chain integration (\cite{WOS:000488423300001}).
+EUROPEAN JOURNAL OF OPERATIONAL RESEARCH (33 papers, 29.73 avg.
+citations) and COMPUTERS \& INDUSTRIAL ENGINEERING (31 papers, 29.55 avg.
+citations) demonstrate balanced output and citations, focusing on operational research (\cite{WOS:000742554100008}) and computational methods for UAV routing (\cite{WOS:000460496000002}).
+Drone logistics research exhibits a dichotomy between high-output, application-focused journals (e.g., Drones with 98 papers) and lower-output, high-impact journals (e.g., Transportation Research Part C with 79.15 avg.
+citations).
+
+\subsection{Discipline}
+The disciplinary focus of drone logistics research has expanded significantly post-2020, reflecting evolving technological and operational priorities.
+Engineering, Electrical \& Electronic remains dominant (63 pre-2020 → 299 post-2020), driven by advancements in UAV hardware, energy efficiency, and IoT integration.
+Transportation Science \& Technology (51 → 265) and Operations Research \& Management Science (56 → 255) show accelerated growth, emphasizing route optimization and hybrid truck-drone coordinated systems.
+Emerging disciplines post-2020 include Management (127) and Remote Sensing (103), highlighting a shift toward strategic logistics governance and geospatial applications.
+The rise of Computer Science, Artificial Intelligence (26 → 108) and Remote Sensing underscores the field’s pivot toward data-driven decision-making, such as AI-enhanced routing and dynamic fleet coordination (\cite{WOS:000742554100008}).
+This evolution reflects drone logistics' maturation from technical feasibility (pre-2020) to multidisciplinary scalability (post-2020), bridging engineering innovations with managerial and computational advancements.
 

### 2025-05-15 latex/draft.tex
更新论文

@@
 \usepackage{ragged2e}  % 文本对齐优化
+\usepackage{float}
 
@@
 \graphicspath{{images/}} % 指定图片路径
+
+\usepackage{subcaption}  % 关键宏包必须加载
+\usepackage{geometry}
+\geometry{a4paper, margin=1.5cm}
+
+% 正确定义子表格模板
+\newcommand{\metricstable}[3]{%
+  \begin{minipage}{0.32\textwidth}
+  \centering
+  \begin{tabularx}{\linewidth}{@{} >{\raggedright\arraybackslash}X r @{}}
+    \toprule
+    \textbf{Institution} & \textbf{#2} \\
+    \midrule
+    #3
+    \bottomrule
+  \end{tabularx}
+  \end{minipage}
+}
 
@@
 
+\begin{table}[htbp]
+  \centering
+  \caption{Top 10 Institutions by Total Citations}
+  \label{tab:citations}
+  \begin{tabularx}{0.9\textwidth}{@{} >{\raggedright}X r @{}}
+    \toprule
+    Institution & Total Citations \\
+    \midrule
+    Sejong University & 1712 \\
+    Auburn University & 1062 \\
+    Purdue University & 1041 \\
+    University System of Maryland & 947 \\
+    University of Maryland & 883 \\
+    York University - Canada & 863 \\
+    State University System of Florida & 821 \\
+    University of Calgary & 807 \\
+    State University of New York (SUNY) System & 798 \\
+    Erasmus University Rotterdam & 763 \\
+    \bottomrule
+  \end{tabularx}
+\end{table}
+
+%% 表2：论文数量排名
+\begin{table}[htbp]
+  \centering
+  \caption{Top 10 Institutions by Publications} 
+  \label{tab:publications}
+  \begin{tabularx}{0.9\textwidth}{@{} >{\raggedright}X r @{}}
+    \toprule
+    Institution & Publications \\
+    \midrule
+    Hong Kong Polytechnic University & 42 \\
+    Nanjing University of Aeronautics \& Astronautics & 33 \\
+    Beihang University & 28 \\
+    Sejong University & 27 \\
+    National University of Defense Technology - China & 26 \\
+    Nanyang Technological University & 22 \\
+    Chinese Academy of Sciences & 21 \\
+    Tsinghua University & 20 \\
+    Purdue University & 19 \\
+    University System of Maryland & 19 \\
+    \bottomrule
+  \end{tabularx}
+\end{table}
+
+%% 表3：H指数排名 
+\begin{table}[htbp]
+  \centering
+  \caption{Top 10 Institutions by H-index}
+  \label{tab:hindex}
+  \begin{tabularx}{0.9\textwidth}{@{} >{\raggedright}X r @{}}
+    \toprule
+    Institution & H-index \\
+    \midrule
+    Sejong University & 19 \\
+    Hong Kong Polytechnic University & 14 \\
+    University of New South Wales Sydney & 13 \\
+    Nanyang Technological University & 13 \\
+    National University of Defense Technology - China & 12 \\
+    Kyung Hee University & 11 \\
+    Northwestern Polytechnical University & 11 \\
+    Purdue University & 10 \\
+    University System of Maryland & 10 \\
+    University of Missouri System & 10 \\
+    \bottomrule
+  \end{tabularx}
+\end{table}
+
 \subsection{Sources}
@@
 Subsequent examination of highly cited articles in Drones suggests a focus on rapid dissemination of applied or technical studies (\cite{WOS:000682822500001, WOS:000682822500021}).
-SUSTAINABILITY (57 papers, 16.88 avg.
+Sustainability (57 papers, 16.88 avg.
 citations) ranks second in publication volume, reflecting its role in hosting interdisciplinary studies on drone logistics' environmental and societal impacts (\cite{WOS:000531558100214, WOS:000428567100315}).
-IEEE TRANSACTIONS ON INTELLIGENT TRANSPORTATION SYSTEMS (57 papers, 28.40 avg.
-citations) matches SUSTAINABILITY in output but achieves higher citations, indicative of its focus on routing innovations (\cite{WOS:000658360600026}) and UAV integration into adaptive traffic systems (\cite{WOS:000684003100038}).
-TRANSPORTATION RESEARCH PART C-EMERGING TECHNOLOGIES (53 papers) achieves the highest average citations (79.15) in this category, reflecting its prominence in publishing high-impact applied optimization studies (\cite{WOS:000353871700006, WOS:000425566000035}).
-IEEE ACCESS (46 papers, 16.00 avg.
-citations) and APPLIED SCIENCES-BASEL (38 papers, 7.50 avg.
-citations) prioritize rapid dissemination of applied research, with IEEE ACCESS showing marginally higher citation influence due to its engineering-focused scope.
-TRANSPORTATION RESEARCH PART E-LOGISTICS AND TRANSPORTATION REVIEW (36 papers, 34.31 avg.
+IEEE Transactions on Intelligent Transportation Systems (57 papers, 28.40 avg.
+citations) matches Sustainability in output but achieves higher citations, indicative of its focus on routing innovations (\cite{WOS:000658360600026}) and UAV integration into adaptive traffic systems (\cite{WOS:000684003100038}).
+Transportation Research Part C: Emerging Technologies (53 papers) achieves the highest average citations (79.15) in this category, reflecting its prominence in publishing high-impact applied optimization studies (\cite{WOS:000353871700006, WOS:000425566000035}).
+IEEE Access (46 papers, 16.00 avg.
+citations) and Applied Sciences-Basel (38 papers, 7.50 avg.
+citations) prioritize rapid dissemination of applied research, with IEEE Access showing marginally higher citation influence due to its engineering-focused scope.
+Transportation Research Part E: Logistics and Transportation Review (36 papers, 34.31 avg.
 citations) publishes strategic analyses of drone logistics' cost-efficiency and supply chain integration (\cite{WOS:000488423300001}).
-EUROPEAN JOURNAL OF OPERATIONAL RESEARCH (33 papers, 29.73 avg.
-citations) and COMPUTERS \& INDUSTRIAL ENGINEERING (31 papers, 29.55 avg.
+European Journal of Operational Research (33 papers, 29.73 avg.
+citations) and Computers \& Industrial Engineering (31 papers, 29.55 avg.
 citations) demonstrate balanced output and citations, focusing on operational research (\cite{WOS:000742554100008}) and computational methods for UAV routing (\cite{WOS:000460496000002}).
@@
 citations).
+
+\begin{table}[htbp]
+  \centering
+  \caption{Top Journals in Drone Logistics Research (2018-2023)}
+  \label{tab:journals}
+  \begin{tabularx}{0.9\textwidth}{@{} >{\raggedright}X r r r @{}}
+    \toprule
+    \textbf{Journal} & \textbf{Pubs.} & \textbf{Total Cites} & \textbf{Cites/Paper} \\
+    \midrule
+    Drones & 98 & 719 & 7.34 \\
+    Sustainability & 57 & 962 & 16.88 \\
+    IEEE Transactions on Intelligent Transportation Systems & 57 & 1619 & 28.40 \\
+    Transportation Research Part C: Emerging Technologies & 53 & 4195 & 79.15 \\
+    IEEE Access & 46 & 736 & 16.00 \\
+    Applied Sciences-Basel & 38 & 285 & 7.50 \\
+    Transportation Research Part E: Logistics and Transportation Review & 36 & 1235 & 34.31 \\
+    European Journal of Operational Research & 33 & 981 & 29.73 \\
+    Computers \& Industrial Engineering & 31 & 916 & 29.55 \\
+    Sensors & 30 & 533 & 17.77 \\
+    \bottomrule
+  \end{tabularx}
+
+  \vspace{0.5em}
+  \raggedright\footnotesize
+\end{table}
+
+\FloatBarrier
 
@@
 This evolution reflects drone logistics' maturation from technical feasibility (pre-2020) to multidisciplinary scalability (post-2020), bridging engineering innovations with managerial and computational advancements.
+
+\begin{table}[H]
+  \centering
+  \caption{Evolution of High-Frequency Disciplines in Drone Logistics Research}
+  \label{tab:discipline_evolution}
+
+  \begin{minipage}[t]{0.48\textwidth}
+  \centering
+  \begin{tabularx}{\linewidth}{@{} >{\raggedright}X r @{}}
+    \toprule
+    \multicolumn{2}{c}{\textbf{Pre-2021 (2000-2020)}} \\
+    \midrule
+    \textbf{Discipline} & \textbf{Frequency} \\
+    \midrule
+    Engineering, Electrical \& Electronic & 63 \\
+    Operations Research \& Management Science & 56 \\
+    Transportation Science \& Technology & 51 \\
+    Telecommunications & 44 \\
+    Computer Science, Information Systems & 40 \\
+    Transportation & 36 \\
+    Robotics & 27 \\
+    Computer Science, Artificial Intelligence & 26 \\
+    Computer Science, Interdisciplinary Applications & 17 \\
+    Engineering, Civil & 17 \\
+    \bottomrule
+  \end{tabularx}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[t]{0.48\textwidth}
+  \centering
+  \begin{tabularx}{\linewidth}{@{} >{\raggedright}X r @{}}
+    \toprule
+    \multicolumn{2}{c}{\textbf{Post-2021 (2021-2023)}} \\
+    \midrule
+    \textbf{Discipline} & \textbf{Frequency} \\
+    \midrule
+    Engineering, Electrical \& Electronic & 299 \\
+    Transportation Science \& Technology & 265 \\
+    Operations Research \& Management Science & 255 \\
+    Telecommunications & 164 \\
+    Computer Science, Information Systems & 150 \\
+    Transportation & 142 \\
+    Management & 127 \\
+    Engineering, Civil & 126 \\
+    Computer Science, Artificial Intelligence & 108 \\
+    Remote Sensing & 103 \\
+    \bottomrule
+  \end{tabularx}
+  \end{minipage}
+
+  \vspace{0.5em}
+  \raggedright\footnotesize
+\end{table}
+
+\FloatBarrier
 

### 2025-05-15 calculate_by_source.py

@@ -53,19 +53,19 @@ def generate_report(journal_data, top_n=20):
         print(f"\n▨ 期刊: {journal}")
         print(f"  发文量: {data['count']} 篇")
         print(f"  总被引: {data['total_citations']} 次")
-        print(f"  篇均被引: {data['avg_citations']:.1f} 次")
+        print(f"  篇均被引: {data['avg_citations']:.2f} 次")
 
-        print("\n  高被引论文TOP5:")
-        for idx, art in enumerate(data['top_articles'], 1):
-            print(f"  {idx}. [{art['citations']}次] {art['title']}")
-            print(f"     作者: {', '.join(art['authors'])}")
-            if art['abstract']:
-                print(f"     摘要: {art['abstract']}")
+        # print("\n  高被引论文TOP5:")
+        # for idx, art in enumerate(data['top_articles'], 1):
+        #     print(f"  {idx}. [{art['citations']}次] {art['title']}")
+        #     print(f"     作者: {', '.join(art['authors'])}")
+        #     if art['abstract']:
+        #         print(f"     摘要: {art['abstract']}")
 
     print("\n\n=== 高频期刊统计（按篇均被引） ===")
     for journal, data in sorted_by_avg:
         print(f"\n▨ 期刊: {journal}")
-        print(f"  篇均被引: {data['avg_citations']:.1f} 次")
+        print(f"  篇均被引: {data['avg_citations']:.2f} 次")
         print(f"  发文量: {data['count']} 篇")
         print(f"  总被引: {data['total_citations']} 次")
 

### 2025-05-15 highly_cited_institutions.py

@@ -1,4 +1,5 @@
 import re
+import json
 from collections import defaultdict
 
 # ================== 用户配置区域 ==================
@@ -17,160 +18,182 @@ EXCLUDE_INSTITUTIONS = {
 }
 
 
-# ================== 数据处理函数 ==================
-def clean_institution_name(raw_name):
-    """机构名称清洗"""
-    name = raw_name.strip()
+def process_c3_institutions(c3_data):
+    """处理C3字段并确保单记录内机构去重"""
+    raw_str = ';'.join(c3_data) if isinstance(c3_data, list) else c3_data
+    processed_str = raw_str.replace('\n', ' ')
 
-    # 应用名称映射
-    for old, new in INSTITUTION_MAPPING.items():
-        if name.lower() == old.lower():
-            return new
+    seen = set()  # 单记录去重集合
+    institutions = []
 
-    # 去除系统后缀
-    name = re.sub(r',.*?(System|Campus)\b', '', name, flags=re.IGNORECASE)
-
-    # 统一缩写
-    name = re.sub(r'\bUniv\b', 'University', name, flags=re.IGNORECASE)
-
-    return name
-
-
-def parse_records(file_path):
-    """解析WOS文件"""
-    records = []
-    current_record = []
-    in_record = False
-
-    with open(file_path, 'r', encoding='utf-8') as f:
-        for line in f:
-            line = line.rstrip('\n')
-
-            if re.match(r'^PT\s', line):
-                if in_record:
-                    records.append(current_record)
-                current_record = [line]
-                in_record = True
-            elif in_record and line == 'ER':
-                current_record.append(line)
-                records.append(current_record)
-                current_record = []
-                in_record = False
-            elif in_record:
-                current_record.append(line)
-
-    return records
-
-
-def parse_record(record_lines):
-    """解析单条记录"""
-    data = defaultdict(list)
-    current_field = None
-
-    for line in record_lines:
-        # 检测字段开始
-        if re.match(r'^[A-Z]{1,2}\d?\s', line[:3]):
-            field_code = line[:2]
-            content = line[3:].strip()
-            current_field = field_code
-            data[field_code].append(content)
-        else:
-            # 处理续行内容
-            if current_field:
-                stripped = line.strip()
-                if current_field == 'AU':
-                    # 每个续行视为新作者
-                    data[current_field].append(stripped)
-                else:
-                    # 合并到当前字段
[…]

### 2025-05-15 institutions.py

@@ -234,11 +234,6 @@ def _write_paper_details(f, ranking, title):
 
 
 if __name__ == "__main__":
-    import sys
 
-    if len(sys.argv) != 2:
-        print(f"使用方法: python {sys.argv[0]} <数据文件路径>")
-        sys.exit(1)
-
-    main(sys.argv[1])
+    main('data/data.txt')
     print(f"分析报告已生成至: {OUTPUT_FILE}")
